A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-10-04 sections/methodology/main.tex
Fix nashpy citation
Break lines at 80 characters

Computation of Nash equilibria can be done relatively efficiently using the Lemke Howson algorithm
\cite{LemkeHowson}.
Lemke-Howson uses best response polytopes to get one of the Nash equilibrium of
the game. 
Other algorithms exists that will compute all Nash equilibria but 
for large games the computational complexity becomes problematic.
All game theoretic calculations were done in Python using the Nashpy library 
\cite{axelrodproject}.

@@

Another approach to measuring emergent behaviour is to consider 
the emergence itself and not just stable end points. 
Indeed, some Nash equilibria might not arise naturally. Thus, in order to analyse the strategies played by the two EDs, the learning algorithm:
asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
The two players are modelled as two separate populations where each 
individual in the population is assigned a strategy.
As the game progresses the proportion of each player playing each strategy 
changes based on their previous interactions.
The fitness of each strategy is defined as:

>>>>

Computation of Nash equilibria can be done relatively efficiently using the 
Lemke Howson algorithm~\cite{LemkeHowson}.
Lemke-Howson uses best response polytopes to get one of the Nash equilibrium of
the game. 
Other algorithms exists that will compute all Nash equilibria but 
for large games the computational complexity becomes problematic.
All game theoretic calculations were done in Python using the Nashpy library 
\cite{thenashpyproject}.

@@

Another approach to measuring emergent behaviour is to consider 
the emergence itself and not only stable end points. 
Indeed, some Nash equilibria might not arise naturally. 
Thus, in order to analyse the strategies played by the two EDs, the learning 
algorithm: asymmetric replicator dynamics is 
used~\cite{asymmetricreplicatordynamics}.
The two players are modelled as two separate populations where each 
individual in the population is assigned a strategy.
As the game progresses the proportion of each player playing each strategy 
changes based on their previous interactions.
The fitness of each strategy is defined as:
